Are we living in a depressive society?

### 2024-04-05 outputs/paper/paper.qmd
commit

@@

# Load necessary libraries
library(tidyverse)
library(lubridate)

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Overall_trends.csv"))

@@

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))

@@

# Load necessary libraries
library(tidyverse)
library(lubridate)
library(here)
library(ggrepel)  # For better label placement

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Sex_subgroup_trends.csv"))

@@

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Race_subgroup_trends.csv"))

@@

# Define the path to the data file and load it
data <- read.csv(file = here::here("outputs/data/Educ_subgroup_trends.csv"))

@@

>>>>

```{r}
#| include: false
#| warning: false
#| message: false

# Load necessary libraries for the paper
library(tidyverse)
library(lubridate)
library(arrow)
library(here)
library(ggrepel)  # For better label placement

@@

# Define the path to the data file and load it
data <- read_parquet(file = here::here("outputs/data/Overall_trends.parquet"))

@@

# Define the path to the data file and load it
data <- read_parquet(file = here::here("outputs/data/Age_subgroup_trends.parquet"))

@@

# Define the path to the data file and load it
data <- read_parquet(file = here::here("outputs/data/Sex_subgroup_trends.parquet"))

@@

# Define the path to the data file and load it
data <- read_parquet(file = here::here("outputs/data/Race_subgroup_trends.parquet"))

@@

# Define the path to the data file and load it
data <- read_parquet(file = here::here("outputs/data/Educ_subgroup_trends.parquet"))

@@

What is done in this paper? 
What is something that we learn about the world? 
What is another thing that we learn about the world? 
What are some weaknesses of what was done? 
What is left to learn or how should we proceed in the future?
